Resultados por município

### 2023-03-19 code/biclarwww/municipio_index.Rmd
colors of existing networks

  leaflet::addLegend(
    "bottomright",
    colors = "#E3879E", 
    labels = "Planeada",
    group = "Rede Ciclável planeada"
  ) %>%
    leaflet::addLegend(
    "bottomright",
    colors = "#4d4d4d", 
    labels = "Existente dedicada",
    group = "Rede Ciclável existente"
  ) %>%
  leaflet::addLayersControl(baseGroups = c("Basemap cinza", "OpenStreetMap", "Satélite"),
                            overlayGroups = c("Potencial 4% - direto", "Potencial 10% - direto", 
                                              "Potencial 4% - seguro", "Potencial 10% - seguro",
                                              "Rede Ciclável planeada", "Rede Ciclável existente"),
                            options = layersControlOptions(collapsed = FALSE)) %>% 
  leaflet::hideGroup(c("Potencial 10% - direto", "Potencial 4% - seguro", "Potencial 10% - seguro",
                       "Rede Ciclável planeada", "Rede Ciclável existente"))

>>>>

  leaflet::addLegend(
    "bottomright",
    colors = "#E3879E", 
    labels = "Planeada",
    group = "Rede Ciclável planeada"
  ) %>%
    leaflet::addLegend(
    "bottomright",
    colors = "#1A7832", 
    labels = "Existente dedicada",
    group = "Rede Ciclável existente"
  ) %>%
  leaflet::addLayersControl(baseGroups = c("Basemap cinza", "OpenStreetMap", "Satélite"),
                            overlayGroups = c("Potencial 4% - direto", "Potencial 10% - direto", 
                                              "Potencial 4% - seguro", "Potencial 10% - seguro",
                                              "Rede Ciclável planeada", "Rede Ciclável existente"),
                            options = layersControlOptions(collapsed = FALSE)) %>% 
  leaflet::hideGroup(c("Potencial 10% - direto", "Potencial 4% - seguro", "Potencial 10% - seguro",
                       "Rede Ciclável planeada", "Rede Ciclável existente"))
